---
title: "2017 Annual Report"
output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    vertical_layout: scroll
    logo: img/logo.png
    favicon: img/fav.png
    navbar:
      - { title: "OIPM Home", href: "http://nolaipm.gov", align: right }
---

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
source("annual_report_2017.R")
source("analysis/force/force_by_year.R")
```

Introduction 
===================================== 

### Navigating the report {width=50%}
This website is an interactive version of the statiscal analysis from OIPM's 2017 Annual Report. Analysis is divided into these sections:

1. [Use of Force](#use-of-force)
2. [Complaints & Discipline](#complaints-and-discipline)
3. [Officer Demographics](#officer-demographics)
4. [Body-worn camera adherence](#bwc-adherence)

### Reproducing this report

#### tl;dr
```
# Clone repo
git clone https://github.com/marvinmarnold/oipm_annual_report

# Open in R then run
setwd("/path/to/repo")
rmarkdown::render_site()
```

#### Source
The data and scripts used to generate this website are available [here](https://github.com/marvinmarnold/oipm_annual_report).

#### Dependencies
The report was written in Rmarkdown using Rstudio and depends on the following dependencies that can be installed using `install.packages("LIBRARY_NAME")`:

- dplyr
- tidyr
- ggplot2
- rmarkdown
- flexdashboard
- plotly

#### Build and run
Once you have all the dependencies installed, you can clone the repository and use Knit in Rstudio to compile `index.Rmd`
in the project's root.

Use of force
===================================== 

### FTN vs UOF
FTN stands for “force tracking number”. It is the designation given to track the entirety
of an interaction between NOPD and one or more individuals wherein force was used.

A single FTN corresponds to one or more UOF. If Officer A and Officer B both use their
hands against Individual C, the result would be one FTN, corresponding to two UOFs
(one for each officer). The same pattern would apply if there were multiple types of
force used or multiple individuals that force was used on.

This report will always clearly label whether FTN or UOF is being used for a particular
analysis but the onus is on the reader to remain vigilant of the distinction.

### FTN & UOF in 2017 by month

### Use of force by year
```{r}
force.by.year
```

Complaints and discipline
=====================================

Officer demographics
===================================== 

BWC adherence
===================================== 