---
title: "2017 Annual Report"
output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    vertical_layout: scroll
    logo: img/logo.png
    favicon: img/fav.png
    navbar:
      - { title: "OIPM Home", href: "http://nolaipm.gov", align: right }
---

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
source("annual_report_2017.R")
source("analysis/force/force_by_year.R")
source("analysis/force/force_by_month.R")
source("analysis/force/uof_by_type.R")
```

Introduction 
===================================== 

### Navigating the report {width=50%}
This website is an interactive version of the statiscal analysis from OIPM's 2017 Annual Report. Analysis is divided into these sections:

1. [Use of Force](#use-of-force)
2. [Complaints & Discipline](#complaints-and-discipline)
3. [Officer Demographics](#officer-demographics)
4. [Body-worn camera adherence](#bwc-adherence)

### Reproducing this report

#### tl;dr
```
git clone https://github.com/marvinmarnold/oipm_annual_report
Rscript run.R
```

#### Source
The data and scripts used to generate this website are available [here](https://github.com/marvinmarnold/oipm_annual_report).

#### Dependencies
The report was written in Rmarkdown using Rstudio and depends on the following dependencies that can be installed using `install.packages("LIBRARY_NAME")`:

- dplyr
- tidyr
- ggplot2
- rmarkdown
- flexdashboard
- plotly
- pandoc (read troubleshooting notes)

#### Build and run
Once you have all the dependencies installed, you can clone the repository and use Knit in Rstudio to compile `index.Rmd`
in the project's root.

#### Troubleshooting
If you have trouble with Pandoc on Linux, check out [these instructions](https://github.com/rstudio/rmarkdown/blob/master/PANDOC.md#newer-systems-debianubuntufedora).

Use of force
===================================== 

### FTN vs UOF
FTN stands for “force tracking number”. It is the designation given to track the entirety
of an interaction between NOPD and one or more individuals wherein force was used.

A single FTN corresponds to one or more UOF. If Officer A and Officer B both use their
hands against Individual C, the result would be one FTN, corresponding to two UOFs
(one for each officer). The same pattern would apply if there were multiple types of
force used or multiple individuals that force was used on.

This report will always clearly label whether FTN or UOF is being used for a particular
analysis but the onus is on the reader to remain vigilant of the distinction.

### Use of force by year

Force jumps between 2014 and 2015 because of new rules about what constitutes force. 
UOF has been rising but FTN about steady. More <officers, victims, types of force> used per force incident.
2015 is the first year that the database that we access (IAPro) was used. Before then, we have to rely on
historic numbers from NOPD.

Furthermore, 2017 is the first year th OIPM has had access to the underlying database. Now that we have access
we find discrepancies with what NOPD previously reported to us. 

As of this writing, there are no major differences in FTNs in 2015

```{r, fig.height = 8}
p.force.by.year
```

### FTN & UOF in 2017 by month
UOF and FTN both peak in Feb and Aug. This corresponds with Mardi Gras and the summer.
UOF per FTN ranges from 2.6 - 4.5.

TODO: What is driving UOF most: citizens, types of force, num officers

```{r, fig.height = 5}
p.force.by.month
```

### Force by level and type of force
```{r, fig.height = 7}
p.uof.by.type
```

Complaints and discipline
=====================================

Officer demographics
===================================== 

BWC adherence
===================================== 